\pkg{cubble}: An R Package for Structuring Spatio-temporal Data

### 2021-12-16 main.Rmd
interactive graphics

```{r interactive-linking, echo = FALSE, out.width="100%", out.height="30%", fig.cap = "sdfasd"}
knitr::include_graphics(here::here("figures/linking.png"))
```

```{r interactive-popup, echo = FALSE, out.width="50%", out.height="30%", fig.cap = "sdfasd"}
knitr::include_graphics(here::here("figures/popup.png"))
```

>>>>

```{r interactive-linking, echo = FALSE, out.width="100%", out.height="25%", fig.cap = "sdfasd"}
knitr::include_graphics(here::here("figures/linking.png"))
```

```{r interactive-popup, echo = FALSE, out.width="50%", out.height="30%", fig.cap = "sdfasd", fig.show='hold'}
knitr::include_graphics(here::here("figures/popup-tas.png"))
knitr::include_graphics(here::here("figures/popup-mid.png"))
knitr::include_graphics(here::here("figures/popup-north.png"))
```

### 2021-12-16 main.tex
interactive graphics

{\centering \includegraphics[width=1\linewidth,height=0.3\textheight]{/Users/sherryzhang/Documents/research/paper-cubble/figures/linking}

@@

{\centering \includegraphics[width=0.5\linewidth,height=0.3\textheight]{/Users/sherryzhang/Documents/research/paper-cubble/figures/popup}

>>>>

{\centering \includegraphics[width=1\linewidth,height=0.25\textheight]{/Users/sherryzhang/Documents/research/paper-cubble/figures/linking}

@@

{\centering \includegraphics[width=0.5\linewidth,height=0.3\textheight]{/Users/sherryzhang/Documents/research/paper-cubble/figures/popup-tas} \includegraphics[width=0.5\linewidth,height=0.3\textheight]{/Users/sherryzhang/Documents/research/paper-cubble/figures/popup-mid} \includegraphics[width=0.5\linewidth,height=0.3\textheight]{/Users/sherryzhang/Documents/research/paper-cubble/figures/popup-north}
